---
title: "Mesquite Phenology Example"
output: rmarkdown::html_vignette
---

First load the `phenometR` and `tidyverse` packages.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(phenometR)
```


This will pull data for all mesquites using it's species code. Then filter it to the open flowers (`DS_08`) and leaves (`DS_02`) phenophases, then to just three of the sites (`GI`,`P9`, and `SC`), and finally only rows with status 0, or 1 to exclude null (-99) values. If you are running this for the first time it will ask for the database username and password. 

```{r}
pros_glan = get_species_phenophase('PRGL') %>%
  filter(PHENOPHASE %in% c('DS_08','DS_02')) %>%
  filter(SITE_CODE %in% c('GI','P9','SC')) %>%
  filter(STATUS %in% c(0,1))  
```

Add in a `week` column to get the mean numbers of plants with leaves or flowers per week.

```{r message=FALSE, warning=FALSE}
pros_glan = pros_glan %>%
  mutate(week = lubridate::week(DATE)) %>%
  group_by(SITE_CODE, PHENOPHASE, YEAR, week) %>%
  summarise(percent_present = mean(STATUS)) %>%
  ungroup()
```

And plot it. With sites as rows, the two phenophases as columns, and different colors as years. 

```{r fig.width=14, fig.height=14}
ggplot(pros_glan, aes(x=week, y=percent_present, color=as.factor(YEAR))) +
  geom_point() +
  geom_line() + 
  scale_color_viridis_d() + 
  facet_wrap(SITE_CODE~PHENOPHASE, ncol=2) +
  theme_bw(20)
```

